Stock enhancement undermines community stability

### 2022-02-03 rmd/manuscript.Rmd
Update manuscript.Rmd

Human demands for natural resources are ever-increasing, such that active interventions are critical to the sustainable management of fisheries, forestry, and wildlife [@laikreCompromisingGeneticDiversity2010]. Captive breeding is common to enhance wild populations of diverse plant and animal taxa [@snyderLimitationsCaptiveBreeding1996; @laikreCompromisingGeneticDiversity2010]. Although there is growing recognition that releases of captive-bred organisms (hereafter, "stock enhancement") entail ecological risks (e.g., the accumulation of deleterious alleles) [@arakiGeneticEffectsCaptive2007; @krkosekDecliningWildSalmon2007], this method is still pervasive in conservation [@snyderLimitationsCaptiveBreeding1996] and natural resource management [@laikreCompromisingGeneticDiversity2010]. In fisheries, for example, billions of hatchery individuals are released annually across the globe [@kitadaEconomicEcologicalGenetic2018]. The widespread use of captive breeding is perhaps because of the "myth" that demographic benefits of released individuals may exceed the associated risks.

Current debates, however, overlook the fact that we have rarely assessed the community-wide impact of stock enhancement. Species are all embedded in the complex web of interacting organisms, and the stable coexistence of competing species through density-dependent feedback underpins emergent stability of ecological communities [@tilmanEcologicalConsequencesChanges1999a; @carrollNicheFitnessDifferences2011a; @loreauDoesFunctionalRedundancy2004]. Stock enhancement may disrupt the sensitive balance of species interactions because it introduces unnaturally high numbers of individuals into the wild [@weberInteractionsHatcheryWild2003; @careyNativeInvadersChallenges2012]. Hence, this form of species management may intervene in the ecological process that allows competing species to coexist, ultimately degrading the long-term community stability. Evidence for this hypothesis is lacking, however.

Here, we use a simple theory to show that stock enhancement undermines long-term community stability, which we define as the relative size of fluctuations in total community density over time [@tilmanEcologicalConsequencesChanges1999a]. Our theory illuminates that stock enhancement interferes with the internal regulation process of self-sustainable communities, compromising the stabilizing mechanism emerging from species niche differences. The present study further demonstrates the relevance of this general theory to natural systems by showing its congruence with Japanese stream fish communities, where \>10 million hatchery masu salmon (*Oncorhynchus masou masou*) are released annually for fisheries, recreation, and conservation purposes [@kitadaLessonsJapanMarine2020].

We employed a multispecies Ricker model [@fowlerSpeciesDynamicsAlter2012] to simulate community dynamics with the selective stock enhancement of a constituent species (species 1). Specifically, population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:

@@

As predicted, stream fish communities showed greater temporal fluctuations (higher CV) in watersheds with intensive stocking (**Figure 1B**). The effect was striking in its magnitude, almost doubling the CV at the highest level of stocking (**Figure 1B**). Our analysis strongly supported the positive relationship between the CV and the number of releases (**Figure 2**), in which the probability of the regression coefficient being positive was `r op(df_beta$all$prob_positive[df_beta$all$response == "cv"])` (**Table S8**). This pattern was associated with the reduced long-term average of the total community density and fewer species richness (**Figure 1B and 2**), and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figure 1B and 2;** see **Tables S8-S10** for full statistics). In the meantime, the SDs had vague relationships with stock enhancement (**Figure 1B and 2**).

@@

We cannot exclude the possibility that spurious correlations drove our results. However, the protected watersheds preserve nearly intact landscapes (average forest coverage: `r round(df_env$frac_forest, 2) * 100`%) with strict regulations of human activities (e.g., exploitation, construction of in-stream structures); therefore, it is difficult to envision that unmeasured human influences caused the observed relationships. Further, we have statistically controlled natural variation in environmental factors (see **Materials and Methods** and **Tables S8-S10**). This unique setup may have helped uncover the close agreement between theory and empirical patterns.

>>>>

Human demands for natural resources are ever-increasing, such that active interventions are critical to the sustainable management of fisheries, forestry, and wildlife [@laikreCompromisingGeneticDiversity2010]. Captive breeding is common to enhance wild populations of diverse plant and animal taxa [@snyderLimitationsCaptiveBreeding1996; @laikreCompromisingGeneticDiversity2010]. Although there is growing recognition that releases of captive-bred organisms (hereafter, "stock enhancement") entail ecological risks (e.g., the accumulation of deleterious alleles) [@arakiGeneticEffectsCaptive2007; @krkosekDecliningWildSalmon2007], this method is still pervasive in conservation [@snyderLimitationsCaptiveBreeding1996] and natural resource management [@laikreCompromisingGeneticDiversity2010]. In fisheries, for example, billions of hatchery individuals are released annually across the globe [@kitadaEconomicEcologicalGenetic2018]. The widespread use of captive breeding is perhaps because of the "myth" that the demographic benefits of released individuals may exceed the associated risks.

Current debates, however, overlook the fact that we have rarely assessed the community-wide impact of stock enhancement. Species are all embedded in the complex web of interacting organisms, and the stable coexistence of competing species through density-dependent feedback underpins the emergent stability of ecological communities [@tilmanEcologicalConsequencesChanges1999a; @carrollNicheFitnessDifferences2011a; @loreauDoesFunctionalRedundancy2004]. Stock enhancement may disrupt the sensitive balance of species interactions because it introduces unnaturally high numbers of individuals into the wild [@weberInteractionsHatcheryWild2003; @careyNativeInvadersChallenges2012]. Hence, this form of species management may intervene in the ecological process that allows competing species to coexist, ultimately degrading the long-term community stability. Evidence for this hypothesis is lacking, however.

Here, we use a simple theory to show that stock enhancement undermines long-term community stability, which we define as the relative size of fluctuations in total community density over time [@tilmanEcologicalConsequencesChanges1999a]. Our theory illuminates that stock enhancement interferes with the internal regulation process of self-sustainable communities, compromising the stabilizing mechanism emerging from species niche differences. The present study further demonstrates the relevance of this general theory to natural systems by showing its congruence with Japanese stream fish communities, where \~10 million hatchery masu salmon (*Oncorhynchus masou masou*) are released annually for fisheries, recreation, and conservation purposes [@kitadaLessonsJapanMarine2020].

We employed a multispecies Ricker model [@fowlerSpeciesDynamicsAlter2012] to simulate community dynamics with the selective stock enhancement of a constituent species (species 1). Specifically, the population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:

@@

As predicted, stream fish communities showed greater temporal fluctuations (higher CV) in watersheds with intensive stocking (**Figure 1B**). The effect was striking in its magnitude, almost doubling the CV at the highest stocking level (**Figure 1B**). Our analysis strongly supported the positive relationship between the CV and the number of releases (**Figure 2**), in which the probability of the regression coefficient being positive was `r op(df_beta$all$prob_positive[df_beta$all$response == "cv"])` (**Table S8**). This pattern was associated with the reduced long-term average of the total community density and fewer species richness (**Figure 1B and 2**), and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figure 1B and 2;** see **Tables S8-S10** for full statistics). In the meantime, the SDs had vague relationships with stock enhancement (**Figure 1B and 2**).

@@

We cannot exclude the possibility that spurious correlations drove our results. However, the protected watersheds preserve nearly intact landscapes (average forest coverage: `r round(mean(df_env$frac_forest), 2) * 100`%) with strict regulations of human activities (e.g., exploitation, construction of in-stream structures); therefore, it is difficult to envision that unmeasured human influences caused the observed relationships. Further, we have statistically controlled natural variation in environmental factors (see **Materials and Methods** and **Tables S8-S10**). This unique setup may have helped uncover the close agreement between theory and empirical patterns.
